Index measures for oak decline severity using phenotypic descriptors

### 2021-01-05 manuscript/manuscript.Rmd
removed redundant manuscript header entry

---
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
    citation_package: natbib
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linespread{2}
  - \linenumbers
bibliography: references.bib
biblio-style: elsarticle-harv
# csl: forest-ecology-and-management.csl
---

>>>>

---
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: false
    citation_package: natbib
fontsize: 12pt
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linespread{2}
  - \linenumbers
bibliography: references.bib
biblio-style: elsarticle-harv
---
